Mapping factors associated with adolescents' emotion dysregulation: A text-mining based systematic review

### 2020-12-17 manuscript.Rmd
Submitted to CD

wordcount         : "5400"
bibliography      : ["veni_sysrev.bib"]
floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man,noextraspace"
output            : papaja::apa6_pdf
knit              : worcs:::cite_essential
---

```{r setup, include = FALSE}
library("papaja")
library(bibliometrix)
library(revtools)
library(bib2df)
library(knitr)
library(kableExtra)
library(cowplot)
run_everything = FALSE
notingraph <- list()
```
<!-- Reviewer suggestions:
Kristin Buss -->

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

<!-- Development and Psychopathology is the most relevant source of articles reviewed herein
Most Relevant Sources

                                                       Sources        Articles
1  DEVELOPMENT AND PSYCHOPATHOLOGY                                         120

on adolescent emotion regulation development is limited27–29. The field is therefore at an impasse: We know that some adolescents are more susceptible to emotion dysregulation than others, but lack tools and theory to identify important predictors of individual development30.
-->

<!-- Emotion regulation in adolescence is important -->
A key developmental challenge in adolescence is acquiring mature emotion
regulation skills [@croneUnderstandingAdolescencePeriod2012;
@zimmermannEmotionRegulationEarly2014]. Emotion regulation is integral to
mental health [@aldaoEmotionregulationStrategiesPsychopathology2010;
@schaferEmotionRegulationStrategies2017; @braetEmotionRegulationChildren2014]
and social functioning [@reindlSocializationEmotionRegulation2016]. For as many
as one in five individuals, adolescence marks the onset of emotion
regulation-related mental illness, which can persist throughout the life course
[see @leeAdolescentMentalHealth2014]. 
It is therefore crucial to identify which
risk factors and environmental hazards render some adolescents more susceptible
to emotional difficulties than others. <!--SH: Main goal of paper -->
Although there is an abundance of empirical work on adolescents' emotion regulation, the literature is somewhat fragmented, because the topic has been investigated from different (sub)disciplines.
As a result, there is a lack of unifying theory,
and intrinsic limitations of narrative reviews prohibit comprehensive coverage of the vast but diffuse literature [@bussTheoriesEmotionalDevelopment2019].

@@

```{r baseline, warning=FALSE, eval = TRUE, out.width = "100%", fig.cap="Correlates of emotion regulation difficulties according to theory (left panel) and narrative reviews (right panel). Transparent circles indicate constructs also represented in the theory."}
knitr::include_graphics("baseline_network.png") 
#fig_svg <- cowplot::ggdraw()+cowplot::draw_image("s1_varimp.svg")
#plot(fig_svg)
keyw <- function(x){
  cat(x)
}
```

@@

The present paper aims to develop a nomological network of the constructs
related to adolescent emotion dysregulation, based on a systematic review of
the literature. A nomological network is a diagrammatic representation of a
phenomenon; a proto-theoretical device that describes relationships between
constructs relevant to the theory [see @alaviAligningTheoryMethodology2018].
It is a precursor to a more
explicit theory of the phenomenon. The present paper uses an inductive approach
to develop this nomological network. <!-- CJ Consider removing the following if the purpose is sufficiently clarified in the introduction -->
First, we conducted a systematic search to
elicit a corpus of relevant literature. Second, we used text mining techniques
to extract relevant constructs from the corpus. Third, we used a dictionary to
pare down the extracted constructs to meaningful superordinate categories.
Fourth, we mapped interrelations between these constructs. Fifth, we classified
contstructs as potential predictors or outcomes.
<!--, and we categorize predictors
by level of analysis-->
<!-- (CJ: Sameroff, which level of biopsychosocial)-->.
<!-- t, using text mining to map potential predictors of adolescent emotion
dysregulation.
identify relevant constructs of adolescents’ emotion regulation development,
and moderators of parents’ role therein. The resulting insights are
consolidated into theory.
The present study intends to map the extant literature
First, I will systematically review predictors currently considered relevant in
the adolescent emotion regulation literature.  -->

@@

All searches were conducted on Web of Science,
the most comprehensive database for which we had permissions for exporting keywords and abstracts.
The search strategy was based on
procedures described by Staaks [@staaksSystematicReviewSearch]. First, we
manually constructed a reference set of 15 articles. Then we constructed a
search string to retrieve these articles from Web of Science. The search was
overly inclusive, returning 29 records.
As these were all highly relevant, we
updated the reference set to include all 29 results.
Next, we tested our search string, which consisted of synonyms of emotion regulation and adolescence: <!--
### Reference set Our reference set is documented in `reference_set.bib`. -->
```
TS=("emotio* regulation" OR "anger regulation" OR "sadness regulation" OR
"emotion* competence" OR "emotion* adjustment" OR "emotio* dysregulation" OR
"anger dysregulation" OR "sadness dysregulation" OR "emotio* problem*" OR
"emotion* maladjustment") AND TS=(adolescent* OR teen* OR pubert* OR youth)
```
This string returned 6653 results, and matched 25 of the 29 records in the
reference set. To match all 29 reference set items,
three additional terms would have to be added to the search string.
Adding the terms `"emotio* socialization" OR "emotio* processes"`, as synonyms for emotion regulation,
would result in 191 more hits, most of which did not meet the inclusion criteria used for screening, as explained below.
Adding the term `"development*"`, as synonym of adolescence, added 3628 new hits,
many of which were not focused on adolescence.
We thus deemed these terms to be overly inclusive, and
proceeded with the original search string above.
```{r readrecs}
filenam <- "recs_6653.RData"
if(!file.exists(filenam)){
  f <- list.files("./recs/18-3-2020/", full.names = TRUE)
  f <- readFiles(f)
  recs <- convert2df(f)
  saveRDS(recs, filenam)
} else {
  recs <- readRDS(filenam)
}
```

@@

```{r removeduplicates}
filenam <- "unique_recs.RData"
if(!file.exists(filenam)){
  recs$doi <- recs$DI
  recs$doi[is.na(recs$doi)] <- paste0("fake", 1:sum(is.na(recs$doi)))
  if(any(duplicated(recs$doi))){
    recs$doi[duplicated(recs$doi)|duplicated(recs$doi, fromLast = T)]
    dup_doi <- duplicated(recs$doi)
    recs <- recs[!dup_doi, ]
  }
  recs$title <- recs$TI
  # locate and extract unique references
  potential_dups <- find_duplicates(recs, match_variable = "title", match_function = "stringdist", threshold = 5, to_lower = TRUE, remove_punctuation = TRUE)
  unique_recs <- extract_unique_references(recs, matches = potential_dups)
  saveRDS(unique_recs, filenam)
  write.csv(data.frame(dup_doi = sum(dup_doi), dup_title = (nrow(recs)-nrow(unique_recs))-sum(dup_doi)), "dups.csv", row.names = FALSE)
} else {
  unique_recs <- readRDS(filenam)
  dups <- read.csv("dups.csv")
}
unique_recs$id_num <- 1:nrow(unique_recs)

@@

```{r prismachart, fig.cap="Record screening flowchart"}
library(tidySEM)

@@

p <- graph_sem(layout = lo, nodes = nodes, edges = edges, angle = 1, rect_height = 1.2, rect_width = 1.3)
ggsave("prismachart.png", p, device = "png")
ggsave("prismachart.svg", p, device = "svg")
knitr::include_graphics("prismachart.png")
```

@@

```{r cache=FALSE}
knitr::read_chunk("study1.R")
```
```{r study1chunk}
```

@@

```{r study1varimp, warning=FALSE, eval = TRUE, out.width = "100%", fig.cap="Document frequency of terms selected for Study 1. Dashed lines and transparent circles indicate constructs also represented in the theory (cf Figure 1)."}
knitr::include_graphics("s1_varimp.png") 
#fig_svg <- cowplot::ggdraw()+cowplot::draw_image("s1_varimp.svg")
#plot(fig_svg)

@@

Many of these excluded constructs represent active ongoing areas of research, including research on *fathers* [@vanlissaRoleFathersMothers2019], *identity* [@campbellFriendsEducationIdentity2019], *friendship* and *social support* [@wangBidirectionalEffectsExpressive2020], *autonomy* [@vrolijkLongitudinalLinkagesFatherunderreview; @brenningPerceivedMaternalAutonomy2015], *sexual risk* [@brownDepressiveSymptomsPredictor2006], and *loneliness* [@spithovenItAllTheir2017].
The fact that these constructs are absent from the graph does not suggest that they are unimportant.
Rather, it indicates that they are not yet well-integrated in the broader literature on adolescents' emotion regulation,
and are therefore prime candidates for future research.<!-- RK: Or could they also suggest that they were relevant in the past, but not any longer? Might it be important to run sensitivity analyses by publication year?
One recommendation for future research might be to study such important but unembedded constructs
in conjunction with other more well-established constructs,
as such an approach might help fill gaps in existing knowledge.-->

@@

```{r, warning=FALSE, message=FALSE}
source("study2.R")
if(run_everything | !file.exists("Study2_lda_dims.txt")) source("LDA_analysis.R")
lda_dims_2 <- read_yaml("Study2_lda_dims.txt")
```
The corpus for this second analysis consisted of the abstracts of the selected articles.
Keywords, as examined in Analysis 1, convey high-quality information because they are carefully chosen by authors to capture the essence of a study.
However, as authors are
typically limited to 5 keywords, some nuance may be lost.
Abstracts, by contrast, offer greater freedom of expression,
but present a greater challenge when it
comes to extracting relevant information.
To perform feature extraction,
we first applied the natural language processing technique "part-of-speech tagging" (POS-tagging), which identifies a word's grammatical function within the sentence context.
Then, we used POS-tagging to retain only nouns and adjectives,
which helps derive more interpretable text mining models [@martinMoreEfficientTopic2015].
Finally, we used stemming to reduce the retained terms to their root form.

>>>>

wordcount         : "6311"
bibliography      : ["veni_sysrev.bib"]
floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man,noextraspace"
output            : papaja::apa6_docx
knit              : worcs:::cite_essential
header-includes:
  - \raggedbottom
---

```{r setup, include = FALSE}
library("papaja")
library(data.table, quietly = TRUE, warn.conflicts = FALSE)
library(knitr)
library(kableExtra)
library(cowplot)
run_everything <- TRUE
notingraph <- list()
keyw <- function(x){
  x
}
```
<!-- Reviewer suggestions:
Kristin Buss -->

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed, echo = FALSE, message = FALSE, warning = FALSE, results="hide")
```

A key developmental challenge in adolescence is acquiring mature emotion
regulation skills [@croneUnderstandingAdolescencePeriod2012;
@zimmermannEmotionRegulationEarly2014]. Emotion regulation is integral to
mental health [@aldaoEmotionregulationStrategiesPsychopathology2010;
@schaferEmotionRegulationStrategies2017; @braetEmotionRegulationChildren2014]
and social functioning [@reindlSocializationEmotionRegulation2016]. For as many
as one in five individuals, adolescence marks the onset of emotion
regulation-related mental illness, which can persist throughout the life course
[see @leeAdolescentMentalHealth2014]. 
It is therefore crucial to identify which
risk factors and environmental hazards render some adolescents more susceptible
to emotional difficulties than others. <!--SH: Main goal of paper -->
Although there is an abundance of empirical work on adolescents' emotion regulation, the literature is somewhat fragmented, because the topic has been investigated from different (sub)disciplines.
As a result, there is a lack of unifying theory,
and intrinsic limitations of narrative reviews prohibit comprehensive coverage of the vast but diffuse literature [@bussTheoriesEmotionalDevelopment2019].

@@

```{r baseline, warning=FALSE, eval = TRUE, results='asis', out.width = "100%", fig.cap="Correlates of emotion regulation difficulties according to theory (left panel) and narrative reviews (right panel). Transparent circles indicate constructs also represented in the theory."}
source("baseline.R", local = TRUE)
knitr::include_graphics("baseline_network.png") 
#fig_svg <- cowplot::ggdraw()+cowplot::draw_image("s1_varimp.svg")
#plot(fig_svg)

@@

The present paper aims to map the constructs
related to adolescent emotion dysregulation, based on a systematic review of
the literature. <!-- CJ Consider removing the following if the purpose is sufficiently clarified in the introduction -->
First, we conducted a systematic search to
elicit a corpus of relevant literature. Second, we used text mining techniques
to extract relevant constructs from the corpus. Third, we used a dictionary to
pare down the extracted constructs to meaningful superordinate categories.
Fourth, we mapped interrelations between these constructs. Fifth, we classified
contstructs as potential predictors or outcomes.
<!--, and we categorize predictors
by level of analysis-->
<!-- (CJ: Sameroff, which level of biopsychosocial)-->.
<!-- t, using text mining to map potential predictors of adolescent emotion
dysregulation.
identify relevant constructs of adolescents’ emotion regulation development,
and moderators of parents’ role therein. The resulting insights are
consolidated into theory.
The present study intends to map the extant literature
First, I will systematically review predictors currently considered relevant in
the adolescent emotion regulation literature.  -->

@@

All searches were conducted on Web of Science,
the most comprehensive database for which we had permissions for exporting keywords and abstracts.
The search strategy was based on
procedures described by Staaks [@staaksSystematicReviewSearch]. First, we
manually constructed a reference set of 15 articles. Then we constructed a
search string to retrieve these articles from Web of Science. The search was
overly inclusive, returning 29 records.
As these were all highly relevant, we
updated the reference set to include all 29 results.
Next, we tested our search string, which consisted of synonyms of emotion regulation and adolescence: <!--
### Reference set Our reference set is documented in `reference_set.bib`. -->
```
TS=("emotio* regulation" OR "anger regulation" OR "sadness regulation" OR
"emotion* competence" OR "emotion* adjustment" OR "emotio* dysregulation" OR
"anger dysregulation" OR "sadness dysregulation" OR "emotio* problem*" OR
"emotion* maladjustment") AND TS=(adolescent* OR teen* OR pubert* OR youth)
```
This string returned 6653 results, and matched 25 of the 29 records in the
reference set. To match all 29 reference set items,
three additional terms would have to be added to the search string.
Adding the terms `"emotio* socialization" OR "emotio* processes"`, as synonyms for emotion regulation,
would result in 191 more hits, most of which did not meet the inclusion criteria used for screening, as explained below.
Adding the term `"development*"`, as synonym of adolescence, added 3628 new hits,
many of which were not focused on adolescence.
We thus deemed these terms to be overly inclusive, and
proceeded with the original search string above.
```{r readrecs}
filenam <- "recs_6653.RData"
if(!file.exists(filenam)){
  library(bibliometrix)
  f <- list.files("./recs/18-3-2020/", full.names = TRUE)
  f <- readFiles(f)
  recs <- convert2df(f)
  saveRDS(recs, filenam)
} else {
  recs <- readRDS(filenam)
}
```

@@

```{r removeduplicates}
filenam <- "unique_recs.RData"
if(!file.exists(filenam)){
  library(revtools)
  recs$doi <- recs$DI
  recs$doi[is.na(recs$doi)] <- paste0("fake", 1:sum(is.na(recs$doi)))
  if(any(duplicated(recs$doi))){
    recs$doi[duplicated(recs$doi)|duplicated(recs$doi, fromLast = T)]
    dup_doi <- duplicated(recs$doi)
    recs <- recs[!dup_doi, ]
  }
  recs$title <- recs$TI
  # locate and extract unique references
  potential_dups <- find_duplicates(recs, match_variable = "title", match_function = "stringdist", threshold = 5, to_lower = TRUE, remove_punctuation = TRUE)
  unique_recs <- extract_unique_references(recs, matches = potential_dups)
  saveRDS(unique_recs, filenam)
  write.csv(data.frame(dup_doi = sum(dup_doi), dup_title = (nrow(recs)-nrow(unique_recs))-sum(dup_doi)), "dups.csv", row.names = FALSE)
} else {
  unique_recs <- readRDS(filenam)
  dups <- read.csv("dups.csv")
}
unique_recs$id_num <- 1:nrow(unique_recs)

@@

```{r prismachart, results='asis', fig.cap="Record screening flowchart"}
library(tidySEM)

@@

p <- graph_sem(layout = lo, nodes = nodes, edges = edges, angle = 1, rect_height = 1.2, rect_width = 1.3, text_size = 4)
ggsave("prismachart.png", p, device = "png")
ggsave("prismachart.svg", p, device = "svg")
knitr::include_graphics("prismachart.png")
```

@@

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(stringr)
library(udpipe)
library(igraph)
library(wordcloud)
library(Matrix)
library(ggplot2)
library(yaml)
source("word_functions.R")
source("circle2.R")

#run_everything = FALSE
study1details <- read_yaml("study1_details.yml")
dict <- read_yaml("yaml_dict.txt")
## Look at POS tags?
if(!isTRUE(tools::md5sum("study1_df.RData") == "042c7d894929b0351f804c1a4b5c5002")){
  recs <- data.table(read.csv("recs_final.csv"))
  if(!is.data.table(recs)){
    browser()
  }
  recs[, "doc" := 1:nrow(recs)]
  study1details <- list(dim_recs = dim(recs))

  # Extract individual words
  df <- lapply(recs$DE, function(x){strsplit(x, split = "; ")[[1]]})
  df <- merge_df(recs, df, "word")

  df[, word := tolower(word)]

  # Clean
  df <- na.omit(df, cols = "word")
  number_docs_words <- c(docs = length(unique(df$doc)), words = length(unique(df$word)))
  yaml::write_yaml(number_docs_words, "study1_number_docs_words.txt")
  # Exclude words
  exclude_terms <- readLines("exclude_terms.txt")
  exclude_these <- unique(unlist(lapply(exclude_terms, grep, x = df$word)))

  df <- df[!exclude_these, ]

  # Categorize words
  res_cat <- cat_words(df$word, dict, handle_dups = "all")
  # Check coding issues
  #res_cat$dup
  #head(res_cat$unmatched)
  df <- merge_df(df, res_cat$words, "word_coded")
  saveRDS(df, "study1_df.RData")
} else {
  df <- readRDS("study1_df.RData")
  number_docs_words <- yaml::read_yaml("study1_number_docs_words.txt")
}

if(run_everything){
  # Frequency of word by doc
  nounbydoc <- df[, list(freq = .N), by = list(doc_id = doc, term = word_coded)]
  # Set frequency to 1; we're not interpreting word frequency, only occurrence
  nounbydoc$freq <- 1

  dtm <- udpipe::document_term_matrix(document_term_frequencies(nounbydoc))

  # Continue plotting word frequency ----------------------------------------

  set.seed(5348)
  dtm_top <- dtm[, select_words(dtm, .975)]
  dtm_top <- dtm_top[rowSums(dtm_top) > 0, ]
  write_yaml(dim(dtm_top), "study1_dtm_top.yml")

  # Wordcloud ---------------------------------------------------------------

  ## Word frequencies
  topterms <- colSums(dtm_top)
  baseline <- readRDS("baseline.RData")

  word_freq <- data.frame(Word = names(topterms), Frequency = topterms, row.names = NULL)
  write.csv(word_freq, "study1_word_freq.csv", row.names = FALSE)
  df_plot <- word_freq
  categ <- read.csv("study1_categorization.csv", stringsAsFactors = FALSE)
  df_plot$cat <- categ$category[match(df_plot$Word, categ$name)]
  df_plot$baseline <- as.character(df_plot$Word %in% baseline)
  df_plot$faded <- df_plot$Word %in% baseline
  df_plot$Word <- pretty_words(df_plot$Word)

  df_plot <- df_plot[order(df_plot$Frequency, decreasing = TRUE), ]
  df_plot$Word <- ordered(df_plot$Word, levels = df_plot$Word[order(df_plot$Frequency)])

  cat_cols <- c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "forestgreen")
  df_plot$cat <- ordered(df_plot$cat, levels = c("Outcome", "Indicator", "Cause", "Protective"))

  write_yaml(df_plot$Word, "s1_words.yml")

  p <- ggplot(df_plot, aes(y = Word, x = Frequency)) +
    geom_segment(aes(x = 0, xend = Frequency,
                     y = Word, yend = Word, linetype = faded), colour = "grey50"
    ) + 
    geom_vline(xintercept = 0, colour = "grey50", linetype = 1) + xlab("Word frequency") +
    geom_point(data = df_plot[df_plot$faded, ], aes(colour = cat), fill = "white", shape = 21, size = 1.5) +
    geom_point(data = df_plot[!df_plot$faded, ], aes(colour = cat, fill = cat), shape = 21, size = 1.5) +
    scale_colour_manual(values = c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "forestgreen"), guide = NULL)+
    scale_fill_manual(values = c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "forestgreen")) +
    scale_x_log10() +
    scale_linetype_manual(values = c("TRUE" = 2, "FALSE" = 1), guide = NULL) +
    theme_bw() + theme(panel.grid.major.x = element_blank(),
                       panel.grid.minor.x = element_blank(), axis.title.y = element_blank(),
                       legend.position = c(.70,.125),
                       legend.title = element_blank(),
                       axis.text.y = element_text(hjust=0, vjust = 0, size = 6))

  svg("s1_varimp.svg", width = 7/2.54, height = 14/2.54)
  eval(p)
  dev.off()

  ggsave("s1_varimp.png", p, device = "png", width = 7, height = 14, units = "cm")

  df_plot$Frequency <- sqrt(df_plot$Frequency)
  ## Visualise them with wordclouds
  p <- quote({
    set.seed(46)
    wordcloud(words = df_plot$Word, freq = df_plot$Frequency, scale = c(2,.4), max.words = 150, rot.per = 0,  random.order = FALSE, colors = brewer.pal(8, "Dark2"))
  })
  svg("study1_wordcloud.svg")
  eval(p)
  dev.off()

  png("study1_wordcloud.png")
  eval(p)
  dev.off()
}

# LDA analysis ------------------------------------------------------------

if(!isTRUE(tools::md5sum("Study1_lda_dims.txt") == "4e2493d4d618020d4acde61dd7864425")){
  library(Rmpfr)
  library(topicmodels)
  library(udpipe)
  library(slam)
  library(tidytext)
  # Functions:
  harmonicMean <- function(logLikelihoods, precision = 2000L) {
    llMed <- median(logLikelihoods)
    as.double(llMed - log(mean(exp(-mpfr(logLikelihoods,
                                         prec = precision) + llMed))))
  }
  BIC <- function(ll, p, n){
    -2 * ll + p * log(n)
  }
  entropy <- function(post_prob){
    1 + (1/(nrow(post_prob) * 
              log(ncol(post_prob)))) * (sum(rowSums(post_prob * 
                                                      log(post_prob + 1e-12))))
  }

  # Preprocessing -----------------------------------------------------------

  #nounbydoc <- df[, list(freq = .N), by = list(doc_id = doc, term = word_coded)]
  df_lda <- nounbydoc #[nounbydoc$term %in% names(dict), ]
  df_lda <- df_lda %>%
    bind_tf_idf(term, doc_id, freq)
  summary(df_lda$tf_idf)
  df_lda <- df_lda[order(df_lda$tf_idf),]

  select_words <- df_lda[!duplicated(df_lda$term), ]
  select_words <- select_words$term[select_words$tf_idf >= median(select_words$tf_idf)]
  df_lda <- df_lda[df_lda$term %in% select_words, ]

  dtm <- udpipe::document_term_matrix(document_term_frequencies(df_lda))

  # dtm <- as.simple_triplet_matrix(dtm)
  # dim(dtm)
  # summary(col_sums(dtm))
  # term_tfidf <- tapply(dtm$v/row_sums(dtm)[dtm$i], dtm$j, mean) * log2(dim(dtm)[1]/col_sums(dtm > 0))
  # summary(term_tfidf)

  yaml::write_yaml(dim(dtm), file = "Study1_lda_dims.txt")

  # Build topic models

  seqk <- seq(2, 20, 1)
  burnin <- 1000
  iter <- 1000
  keep <- 50
  set.seed(44773)
  res_lda <- lapply(seqk, function(k) {
    topicmodels::LDA(
      dtm,
      k = k,
      method = "Gibbs",
      control = list(
        burnin = burnin,
        iter = iter,
        keep = keep
      )
    )
  })

  ll <- sapply(res_lda, function(x){harmonicMean(x@logLiks[-c(1:(burnin/keep))])})

  K = seqk
  N = nrow(dtm)
  M = ncol(dtm)

  parameters <- K*(M-1)+N*(K-1)
  N <- nrow(dtm)
  bics <- BIC(ll, parameters, N)

  entropies <- sapply(res_lda, function(x){entropy(x@gamma)})

  p <- ggplot(data.frame(K = seqk, Entropy = entropies), aes(x = K, y = Entropy)) + geom_path() +
    xlab('Number of topics') +
    scale_y_continuous(limits = c(0,1)) +
    theme_bw()

  ggsave("study1_entropies.png", p, device = "png")
  ggsave("study1_entropies.svg", p, device = "svg")

  p <- ggplot(data.frame(K = seqk, ll = ll), aes(x = K, y = ll)) + geom_path() +
    geom_vline(xintercept = (which.max(ll)+1), linetype = 2) +
    xlab('Number of topics') +
    geom_smooth(method = "lm", formula = y~log(x), se = FALSE)+
    theme_bw()

  ggsave("study1_ll.png", p, device = "png")
  ggsave("study1_ll.svg", p, device = "svg")

  p <- ggplot(data.frame(K = seqk, BIC = bics), aes(x = K, y = BIC)) + geom_path() +
    geom_vline(xintercept = (which.min(bics)+1), linetype = 2) +
    xlab('Number of topics') +
    geom_smooth(method = "lm", formula = y~x, se = FALSE)+
    theme_bw()

  ggsave("study1_BIC.png", p, device = "png")
  ggsave("study1_BIC.svg", p, device = "svg")
}

# Co-occurrence -----------------------------------------------------------

if(run_everything){
  set.seed(52)
  cooc <- select_cooc(create_cooc(dtm_top), q = .975)
  write.csv(as.matrix(cooc), "s1_cooc.csv")
  df_plot <- as_cooccurrence(cooc)
  df_plot <- df_plot[!df_plot$term1 == df_plot$term2, ]
  df_plot <- df_plot[order(df_plot$cooc, decreasing = TRUE), ]

  df_plot$id <- apply(df_plot[, c("term1", "term2")], 1, function(x)paste0(sort(x), collapse = ""))
  df_plot <- df_plot[!duplicated(df_plot$id), ]

  # Write study details -----------------------------------------------------

  write_yaml(study1details, "study1_details.yml")

  # Create network ----------------------------------------------------------

  edg <- df_plot
  edg$width = edg$cooc

  vert <- data.frame(name = names(topterms), label = pretty_words(names(topterms)), size = topterms)
  vert <- vert[vert$name %in% unique(c(edg$term1, edg$term2)), ]

  categ <- read.csv("study1_categorization.csv", stringsAsFactors = FALSE)
  if(any(!vert$name %in% categ$name)){
    write.table(vert$name[!vert$name %in% categ$name], "clipboard", sep = "\n", row.names = FALSE, col.names= FALSE)
    stop("Please re-categorize missing vertices.")
  } 
  vert$Category <- categ$category[match(vert$name, categ$name)]
  vert$faded <- vert$name %in% baseline

  cat_cols <- c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "olivedrab2")
  vert$color <- cat_cols[vert$Category]
  vert$frame.color <- cat_cols[vert$Category]
  vert$color[vert$faded] <- "#FFFFFF"

  vert$size <- scales::rescale(log(vert$size), c(4, 12))
  g <- graph_from_data_frame(edg, vertices = vert,
                             directed = FALSE)

  # edge thickness
  E(g)$width <- scales::rescale(sqrt(E(g)$width), to = c(2, 8))

  dysreg_vertex = which(names(V(g)) == "dysregulation")

  edge.start <- ends(g, es=E(g), names = FALSE)[,1]
  edge.end <- ends(g, es=E(g), names = FALSE)[,2]
  E(g)$lty <- c(1, 5)[(!(edge.start == dysreg_vertex|edge.end == dysreg_vertex))+1]

  # Layout
  set.seed(6) #4
  l1 <- l <- layout_with_fr(g)
  l1[,1] <- -1*l1[,1]
  set.seed(64)
  l2 <- layout_in_circle(g, order = shifter(V(g), -3))

  p <- quote({
    # Set margins to 0
    par(mar=c(0,0,0,0),
        mfrow=c(1,2))
    plot(g, edge.curved = 0, layout=l1,
         vertex.label.family = "sans",
         vertex.label.cex = 0.8,
         vertex.shape = "circle2",
         #vertex.frame.color = 'gray40',
         vertex.label.color = 'black',      # Color of node names
         vertex.label.font = 1,         # Font of node names
         vertex.frame.width = 2
    )
    legend(x=-1.1, y=1.1, names(cat_cols), pch=21, col="#777777", pt.bg=cat_cols, pt.cex=2, cex=.8, bty="n", ncol=1)
    plot(g, edge.curved = 0, layout=l2,
         vertex.label.family = "sans",
         vertex.label.cex = 0.8,
         vertex.shape = "circle2",
         #vertex.frame.color = 'gray40',
         vertex.label.color = 'black',      # Color of node names
         vertex.label.font = 1,         # Font of node names
         vertex.frame.width = 2
    )
  })

  # Save files
  png("study1_network1.png", width = 960)
  eval(p)
  dev.off()

  svg("study1_network1.svg", width = 14)
  eval(p)
  dev.off()
}
categ <- read.csv("study1_categorization.csv", stringsAsFactors = FALSE)
word_freq <- read.csv("study1_word_freq.csv", stringsAsFactors = FALSE)
word_graph <- read.csv("s1_cooc.csv", row.names = 1)
notingraph <- word_freq$Word[!word_freq$Word %in% row.names(word_graph)]
notingraph <- categ[categ$name %in% notingraph, ]
cats <- unique(notingraph$category)
notingraph <- lapply(cats, function(x){ 
  out <- notingraph$name[notingraph$category == x]
  out <- pretty_words(out)
  paste0(paste0("*", out[-length(out)], "*", collapse = ", "), ", and *", tail(out, 1), "*")
  })
names(notingraph) <- cats

lda_dims <- read_yaml("Study1_lda_dims.txt")
dtm_top <- read_yaml("study1_dtm_top.yml")
```

@@

```{r study1varimp, warning=FALSE, eval = TRUE, results='asis', out.width = "100%", fig.cap="Document frequency of terms selected for Study 1. Dashed lines and transparent circles indicate constructs also represented in the theory (cf Figure 1)."}
knitr::include_graphics("s1_varimp.png") 
#fig_svg <- cowplot::ggdraw()+cowplot::draw_image("s1_varimp.svg")
#plot(fig_svg)

@@

Many of these excluded constructs represent active ongoing areas of research, including research on *fathers* [@vanlissaRoleFathersMothers2019], *identity* [@campbellFriendsEducationIdentity2019], *friendship* and *social support* [@wangBidirectionalEffectsExpressive2020], *autonomy* [@vrolijkLongitudinalLinkagesFather2020a; @brenningPerceivedMaternalAutonomy2015], *sexual risk* [@brownDepressiveSymptomsPredictor2006], and *loneliness* [@spithovenItAllTheir2017].
The fact that these constructs are absent from the graph does not suggest that they are unimportant.
Rather, it indicates that they are not yet well-integrated in the broader literature on adolescents' emotion regulation,
and are therefore prime candidates for future research.<!-- RK: Or could they also suggest that they were relevant in the past, but not any longer? Might it be important to run sensitivity analyses by publication year?
One recommendation for future research might be to study such important but unembedded constructs
in conjunction with other more well-established constructs,
as such an approach might help fill gaps in existing knowledge.-->

@@

```{r}
source("word_functions.R")
source("circle2.R")
```

```{r}
library(stringr)
library(udpipe)
library(igraph)
library(wordcloud)
library(Matrix)
library(yaml)
library(Rmpfr)
library(topicmodels)
library(udpipe)
library(slam)
library(tidytext)
library(ggplot2)
library(textrank)

if(isTRUE(tools::md5sum("study2_df.RData") == "21abb2622dfd94d8bd3473ed56697f9e")){
  df <- readRDS("study2_df.RData")
} else {
  stop("Note: Study 2 file is out of date. Please run this code manually.")
  recs <- data.table(read.csv("recs_final.csv"))
  if(!is.data.table(recs)){
    browser()
  }
  recs[, "doc" := 1:nrow(recs)]

  recs$AB <- tolower(recs$AB)
  if(!file.exists("english-ewt-ud-2.4-190531.udpipe")) {
    ud_model <- udpipe_download_model(language = "english")
  } else {
    ud_model <- udpipe_load_model("english-ewt-ud-2.4-190531.udpipe")
    ud_model <- udpipe_load_model(ud_model$file)
  }
  udp_res <- udpipe_annotate(ud_model, x = recs$AB, doc_id = recs$doc)
  df <- as.data.table(udp_res)
  saveRDS(df, "study2_df.RData")
}

# LDA analysis ------------------------------------------------------------

if(!isTRUE(tools::md5sum("Study2_lda_dims.txt") == "2d00a24d8b54ac898eec6cd104086a0f")){
  # Functions:
  harmonicMean <- function(logLikelihoods, precision = 2000L) {
    llMed <- median(logLikelihoods)
    as.double(llMed - log(mean(exp(-mpfr(logLikelihoods,
                                         prec = precision) + llMed))))
  }
  BIC <- function(ll, p, n){
    -2 * ll + p * log(n)
  }
  entropy <- function(post_prob){
    1 + (1/(nrow(post_prob) * 
              log(ncol(post_prob)))) * (sum(rowSums(post_prob * 
                                                      log(post_prob + 1e-12))))
  }

  # Preprocessing -----------------------------------------------------------

  # Frequency of word by doc
  nounbydoc <- df[df$upos %in% c("NOUN", "ADJ"), list(freq = .N), by = list(doc_id = doc_id, term = lemma)]
  df_lda <- nounbydoc #[nounbydoc$term %in% names(dict), ]
  df_lda <- df_lda %>%
    bind_tf_idf(term, doc_id, freq)
  summary(df_lda$tf_idf)

  select_words <- df_lda[!duplicated(df_lda$term), ]
  select_words <- select_words$term[select_words$tf_idf >= median(select_words$tf_idf)]
  df_lda <- df_lda[df_lda$term %in% select_words, ]

  dtm <- udpipe::document_term_matrix(document_term_frequencies(df_lda))
  yaml::write_yaml(dim(dtm), file = "Study2_lda_dims.txt")

  # Build topic models
  seqk <- seq(2, 20, 1)
  burnin <- 1000
  iter <- 1000
  keep <- 50
  set.seed(44773)
  res_lda <- lapply(seqk, function(k) {
    topicmodels::LDA(
      dtm,
      k = k,
      method = "Gibbs",
      control = list(
        burnin = burnin,
        iter = iter,
        keep = keep
      )
    )
  })

  ll <- sapply(res_lda, function(x){harmonicMean(x@logLiks[-c(1:(burnin/keep))])})

  K = seqk
  N = nrow(dtm)
  M = ncol(dtm)

  parameters <- K*(M-1)+N*(K-1)
  N <- nrow(dtm)
  bics <- BIC(ll, parameters, N)

  entropies <- sapply(res_lda, function(x){entropy(x@gamma)})

  p <- ggplot(data.frame(K = seqk, Entropy = entropies), aes(x = K, y = Entropy)) + geom_path() +
    xlab('Number of topics') +
    scale_y_continuous(limits = c(0,1)) +
    theme_bw()

  ggsave("study2_entropies.png", p, device = "png")
  ggsave("study2_entropies.svg", p, device = "svg")
